Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-29 ms.qmd
Re-render

**Running head**: Physiological rate variation in ectotherms
Havird 
## **Abstract**

@@

In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see *Supplementary Materials* @fig-lnrrq10_temp). We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter]. The benefit of this approach is that we could still use $Q_{10}$ as an effect size while statistically correcting for the potential non-linearity that would be expected in the data at high treatment temperatures. Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments. We mean-centered the maximum temperature and included it in our models.

@@

Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`\% of the variance was the result of sampling variability, 95\% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`\%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`\% , 95\% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`\%; Trait Type: `r mean(trait_i2)`\% , 95\% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`\%). Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%). These patterns were similar for $lnVR_{Q_{10}}$ ( see *Supplementary Materials*, @fig-s3).

Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly betweem aquatic and terrestrial habiatats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2"). However, capacity for acclimation depended on the habitat. Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`\% (95\% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`\% (95\% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`\% increase in $lnRR_{Q_{10_{acclimation}}}$ (95\% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).

@@

p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.4, 1.5) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)

@@

@@

### *Comparing relative variance changes: the *lnCVR* ratio*
As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship. As such, the coefficient of variation is often used because it permits standardisation of changes in variance as mean trait values change:

@@

@@

 p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
  ggsave(p_mv, file = "./output/figures/figS5.png", height = 8, width = 8)

  p_mv <- magick::image_read("./output/figures/figS5.png")
  p_mv
```

@@

When measuring plasticity, what is reletavent is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate). Variation in the magnitude of plasticity across studies is captured in our random slope models and is more powerful given that even studies without acute responses measured can be included. We can then estimate the mean difference between acute and acclimation in our meta-regression models while accounting for variation in responses within studies with our random slope. This analysis is the same as if we were to model the difference in acute and acclimation effect sizes within studies instead of each seperately.

We can validate that our main analysis is similar to an analysis that only includes studies with both acute and acclimation responses. To achive this, we need to derive a new effect size that contrasts the difference between acute and acclimation responses within a given study and trait using the following equation:

where, s_{lnRR_{Q_{10_{acute}}}} and s_{lnRR_{Q_{10_{acclimation}}}} is the sampling variance for the acute and acclimation effect sizes, respectively. Again, all notation is defined in @eq-Vlnq10 in the main manuscript.

Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait. Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta. Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c_slope)`, 95\% CI: `r quantile(b_max_temp_c_slope, c(0.025, 0.975))`).

```{r, fig-delta}
#| label: fig-delta
#| fig-cap: "Analysis with $\\Delta lnRR_{Q_{10}}$. Raw effects are weighted by their precision (inverse sampling variance). "

  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       axis.text.y = element_text(angle = 45, size = 24),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top") 
p3_ac_aclim
```

@@

  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       axis.text.y = element_blank(),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")

@@

  ggsave(p3b, filename = "./output/figures/figS6.pdf", width = 11.5, height = 8)

  figs1 <- image_read("./output/figures/figS6.pdf")
  figs1
```

@@

############
# Full fig
############
figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait_vr, filename = "./output/figures/figS7.png", width = 28, height = 8, device = "png")

figbtrait <- magick::image_read("./output/figures/figS7.png")
figbtrait
```

@@

figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figcvr_lh, filename = "./output/figures/figS8.pdf", width = 28, height = 10, device = "pdf")

figcvr_lh <- magick::image_read("./output/figures/figS8.pdf")
figcvr_lh

@@

############
# Full fig
############
figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait, filename = "./output/figures/fig4.png", width = 28, height = 14, device = "png")

figbtrait <- magick::image_read("./output/figures/fig4.png")
figbtrait
```

@@

fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
ggsave(fig2, filename = "./output/figures/figS9.png", height = 20, width = 15)

img_fig2 <- magick::image_read("./output/figures/figS9.png")
img_fig2
```

@@

figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figvrtrait, filename = "./output/figures/figS10.png", height = 20, width = 15)

img_figvrtrait <- magick::image_read("./output/figures/figS10.png")
img_figvrtrait
```

@@

figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figcvrtrait, filename = "./output/figures/figS11.png", height = 20, width = 15)

img_figcvrtrait <- magick::image_read("./output/figures/figS11.png")
img_figcvrtrait
```

@@

figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS12.png")

figS12 <- image_read("./output/figures/figS12.png")
figS12
```

@@

ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS13.pdf")

  p_acf <- image_read("./output/figures/figS13.pdf")
  p_acf 
```

@@

figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS14.png")

figs2 <- image_read("./output/figures/figS14.png")
figs2
```

@@

#### **Performance Curve Simulations**

@@

p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS15.png")

p_sim <- image_read("./output/figures/figS15.png")
p_sim
```

>>>>

**Running head**: Physiological rate variation in ectotherms

## **Abstract**

@@

In addition to the acclimation period, all our models corrected for possible violations of the log-linearity assumption associated with effect size calculations ([@fig-concept]; and see *Supplementary Materials* @fig-lnrrq10_temp). We predicted that, if $lnRR_{Q_{10}}$ and $lnVR_{Q_{10}}$ were not strictly log-linear there would be a decrease in average effect size for studies applying higher temperature treatments, because these temperatures are expected to either converge on or cross the thermal maxima of the performance curve causing reaction rates to decelerate or decrease beyond $T_{op}$ [@michaletz2024hotter]. Given that our data included a wide range of species and habitats, we also included a random slope of maximum temperature that varied across species because we expected that species would vary in their thermal performance curves, which would be reflected in experimental treatments. We mean-centered the maximum temperature and included it in our models.

@@

Results from "Model 1" (see “Meta-Analysis” above) show that effect heterogeneity was high (only `r mean(tot_i2)`\% of the variance was the result of sampling variability, 95\% CI: `r quantile(tot_i2, 0.025)[1]` to `r quantile(tot_i2, 0.975)[1]`\%), and most variance was explained by the specific study and type of trait (Study: `r mean(stdy_i2)`\% , 95\% CI: `r quantile(stdy_i2, 0.025)[1]` to `r quantile(stdy_i2, 0.975)[1]`\%; Trait Type: `r mean(trait_i2)`\% , 95\% CI: `r quantile(trait_i2, 0.025)[1]` to `r quantile(trait_i2, 0.975)[1]`\%). Evolutionary relationships among taxa and species ecology (i.e., species random effect) explained little variation in acute and acclimation responses (Species: `r mean(spp_i2)`\%, 95\% CI: `r quantile(spp_i2, 0.025)[1]` to `r quantile(spp_i2, 0.975)[1]`\%; Phylogeny: `r mean(phylo_i2)`\% , 95\% CI: `r quantile(phylo_i2, 0.025)[1]` to `r quantile(phylo_i2, 0.975)[1]`\%). These patterns were similar for $lnVR_{Q_{10}}$ (see *Supplementary Materials*, @fig-s3).

Physiological rates increased more in terrestrial ectotherms ($\mu$ = `r mean(t_RR_mean)`, 95\% CI: `r quantile(t_RR_mean, 0.025)` to `r quantile(t_RR_mean, 0.975)`) compared to marine ($\mu$ = `r mean(m_RR_mean)`, 95\% CI: `r quantile(m_RR_mean, 0.025)` to `r quantile(m_RR_mean, 0.975)`) and freshwater ectotherms ($\mu$ = `r mean(f_RR_mean)`, 95\% CI: `r quantile(f_RR_mean, 0.025)` to `r quantile(f_RR_mean, 0.975)`), but did not differ significantly between aquatic and terrestrial habitats (Terrestrial - Marine: $\beta$ = `r mean(t_m_rates)`, 95\% CI: `r quantile(t_m_rates, 0.025)` to `r quantile(t_m_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_m_rates))`; Terrestrial - Freshwater: $\beta$ = `r mean(t_f_rates)`, 95\% CI: `r quantile(t_f_rates, 0.025)` to `r quantile(t_f_rates, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(t_f_rates))`) ("Model 2"). However, capacity for acclimation depended on the habitat. Ectotherms in marine and freshwater environments showed partial compensation of physiological rates ([@fig-2]A) amounting to reduced $lnRR_{Q_{10_{acclimation}}}$ of `r abs(mean(change_f))`\% (95\% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r abs(mean(change_m))`\% (95\% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation with a `r abs(mean(change_t))`\% increase in $lnRR_{Q_{10_{acclimation}}}$ (95\% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-2]A).

@@

p1 <- orchard_plot(model1.4, mod = "life.hist", at = list(c_accl_time = 0, habitat = "m"), group = "spp", xlab = TeX("$lnRR_{Q_{10}}$"), condition.lab = "Type", by = "type",  g = FALSE, k = FALSE, angle = 45, branch.size = branch.size, trunk.size = trunk.size) + labs(title = "Marine") + add_theme() + ylim(-0.5, 1.6) + theme(legend.position = "none", axis.text.y = element_blank()) + annotate("text", x = x.pos, y = 1.3, label = TeX(paste0("\\it{k} = ", m_r$k, " (", m_r$spp, ")")), size = size_annot) + annotate("text", x = yloc, y = -0.4, label = TeX(paste0("$\\beta$ = ", m_trait_b$diff, " [", m_trait_b$l95, " to ", m_trait_b$u95, "] ", "$\\,p_{MCMC}$ = ", m_trait_b$p)), hjust = 0, size = 8)

@@

  # Check slope
   b_max_temp_c <- posteriors_3_overall[,"b_max_temp_c"]; pmcmc(b_max_temp_c); mean(b_max_temp_c); quantile(b_max_temp_c, c(0.025, 0.975))

@@

@@

When measuring plasticity, what is relevant is the difference between $lnRR_{Q_{10_{acute}}}$ and $lnRR_{Q_{10_{acclimation}}}$ because this captures the degree to which organisms plastically adjust (or acclimate). Variation in the magnitude of plasticity across studies is captured in our random slope models and is more powerful given that even studies without acute responses measured can be included. We can then estimate the mean difference between acute and acclimation in our meta-regression models while accounting for variation in responses within studies with our random slope. This analysis is the same as if we were to model the difference in acute and acclimation effect sizes within studies instead of each separately.

We can validate that our main analysis is similar to an analysis that only includes studies with both acute and acclimation responses. To achieve this, we need to derive a new effect size that contrasts the difference between acute and acclimation responses within a given study and trait using the following equation:

where, $s_{lnRR_{Q_{10_{acute}}}}$ and $s_{lnRR_{Q_{10_{acclimation}}}}$ is the sampling variance for the acute and acclimation effect sizes, respectively. Again, all notation is defined in @eq-Vlnq10 in the main manuscript.

Using $\Delta lnRR_{Q_{10}}$ for each trait within a study we fit a model that estimated the meta-anlaytic mean effect size for each habitat (freshwater, marine and terrestrial) accounting for acclimation time and maximum temperature as in our main analysis, along with random effects of study, species, phylogeny, and trait. Our analyses given quantitatively and qualitatively similar resuls to our main analysis @fig-delta. Acclimation time did not explain variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_c_accl_time_slope)`, 95\% CI: `r quantile(b_c_accl_time_slope, c(0.025, 0.975))`, p = `r pmcmc(b_c_accl_time_slope)`) and there was weak evidence that maximum temperature explained variation in $\Delta lnRR_{Q_{10}}$ (slope = `r mean(b_max_temp_c)`, 95\% CI: `r quantile(b_max_temp_c, c(0.025, 0.975))`, p = `r pmcmc(b_max_temp_c)`).

```{r, fig-delta}
#| label: fig-delta
#| fig-cap: "Meta-analysis results for $\\Delta lnRR_{Q_{10}}$ across different habitats. Thick bars are 95% confidence intervals (CI) and thin bars 95% prediction intervals (PI). $\\beta$ values are the contrasts between acute and acclimation means within each habitat. $\\mu$ values are the overall meta-analytic means averaged across acute and acclimation types within each habitat type. 95% CI's are indicated within square brackets and raw effects are weighted by their precision (inverse sampling variance). $p_{MCMC}$ values are the posterior probability of the contrast or overall meta-analytic mean being different from zero. k = total number of effect size estimates while the numbers in brackets indicate the number of species.  For ease of visualisation, all the raw data plotted for both acute and acclimation type effect sizes are presented as circles. Raw effects are weighted by their precision (inverse sampling variance). "

  p3_ac_aclim <- p3_ac_aclim + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       axis.text.y = element_text(angle = 45, size = 24),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top")

  ggsave(p3_ac_aclim, filename = "./output/figures/figS5.pdf", width = 11.5, height = 8)

  p3_ac_aclim <- image_read("./output/figures/figS5.pdf")
  p3_ac_aclim

#### **Comparing relative variance changes: the *lnCVR* ratio**
As discussed by @Nakagawa2015-fo there is often a strong mean-variance relationship. As such, the coefficient of variation is often used because it permits standardization of changes in variance as mean trait values change:

@@

 p_mv <-  (mv1 / mv2)  + plot_annotation(tag_levels = "A") + theme(plot.tag = element_text(size = 20))
  ggsave(p_mv, file = "./output/figures/figS6.png", height = 8, width = 8)

  p_mv <- magick::image_read("./output/figures/figS6.png")
  p_mv
```

@@

@@

  p3b <- p3b + theme_classic() + theme(axis.title  = element_text(size = 24),
                                       axis.text = element_text(size = 24),
                                       legend.title = element_text(size = 30),
                               legend.text = element_text(size = 24),
                               title = element_text(size = 24), legend.position = "top") + guides(shape = "none")

@@

  ggsave(p3b, filename = "./output/figures/figS7.pdf", width = 11.5, height = 8)

  figs1 <- image_read("./output/figures/figS7.pdf")
  figs1
```

@@

############
# Full fig
############
figbtrait_vr <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait_vr, filename = "./output/figures/figS8.png", width = 28, height = 8, device = "png")

figbtrait <- magick::image_read("./output/figures/figS8.png")
figbtrait
```

@@

figcvr_lh <-(p3_cvr | p1_cvr | p2_cvr) + plot_annotation(tag_levels = "A") 
ggsave(figcvr_lh, filename = "./output/figures/figS9.pdf", width = 28, height = 10, device = "pdf")

figcvr_lh <- magick::image_read("./output/figures/figS9.pdf")
figcvr_lh

@@

############
# Full fig
############
figbtrait <-(p3 | p1 | p2) / (p3_vr_trait | p1_vr_trait | p2_vr_trait) + plot_annotation(tag_levels = "A") 
ggsave(figbtrait, filename = "./output/figures/figS10.png", width = 28, height = 14, device = "png")

figbtrait <- magick::image_read("./output/figures/figS10.png")
figbtrait
```

@@

fig2 <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A")
ggsave(fig2, filename = "./output/figures/figS11.png", height = 20, width = 15)

img_fig2 <- magick::image_read("./output/figures/figS11.png")
img_fig2
```

@@

figvrtrait <- (ptm_vr / ptf_vr / ptt_vr) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figvrtrait, filename = "./output/figures/figS12.png", height = 20, width = 15)

img_figvrtrait <- magick::image_read("./output/figures/figS12.png")
img_figvrtrait
```

@@

figcvrtrait <- (ptm / ptf / ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(figcvrtrait, filename = "./output/figures/figS13.png", height = 20, width = 15)

img_figcvrtrait <- magick::image_read("./output/figures/figS13.png")
img_figcvrtrait
```

@@

figS12 <- (ps3_1 | ps3_2 | ps3_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figS12, width = 16, height = 5.7, filename = "./output/figures/figS14.png")

figS12 <- image_read("./output/figures/figS14.png")
figS12
```

@@

ggsave(p_acf, width = 18, height = 10, filename = "./output/figures/figS15.pdf")

  p_acf <- image_read("./output/figures/figS15.pdf")
  p_acf 
```

@@

figs2 <- (ps2_1 | ps2_2 | ps2_3) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 20))
ggsave(figs2, width = 11.5, height = 4.8, filename = "./output/figures/figS16.png")

figs2 <- image_read("./output/figures/figS16.png")
figs2
```

@@

#### **Performance curve simulations**

@@

p_sim <- ((sim1 + sim2) / (sim4 + sim3)) +plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 30))
ggsave(p_sim, width = 22.5, height = 18, filename = "./output/figures/figS17.png")

p_sim <- image_read("./output/figures/figS17.png")
p_sim
```
